The first high-redshift Changing Look Quasars

### 2019-11-10 tex/other_tex/CIV_CLQs_20191108.tex
Big, BIG tex/ update

For the BOSS spectrum of J2228+2201 on MJD 56189, some of the data are
``masked'' (i.e. they have {\tt and\_mask} != 0) in the FITS file at
wavelengths $\lesssim$1600\AA\ (rest-frame).  This typically means
there is some potential problem in using those data. However, visual
inspection shows strong broad \civ\ emission, so we disable the check on the mask,
and report the line fits in Table~\ref{tab:LineMeasurement}

\begin{table*}
  \centering
  \input{emission_line_comparison_tab}

  \caption{Line Measurement information for the nine epochs for the 3 quasars.
    Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
    where positive values of $V_{\rm off}$ means the line is blueshifted.
    Equivalent widths are \AA\.  
    Shen11 is \citet{Shen2011}. 
    Ham17 is \citet{Hamann2017}.
    DR12 SAS is the line measurement information from the SDSS DR12 
    Science Archive Server (SAS).
    $^{(a)}$Emission lines of a common ``width group'', in this case,
    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
    the same intrinsic velocity width in the SDSS spectral line fitting
    procedure \citep{Bolton2012}. 
    % $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
    Positive values of Voff means the line is blueshifted.
    % $^{(b)}$Bit 3: FWHM value hits a limit in the fit
    Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
    54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
    $^{(d)}$Emission line modelled with two components.
    The different colours of text are merely for readability.
    }
 \label{tab:LineMeasurements}
\end{table*}

@@

    M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\

@@

        Kozl17 is \citet{Kozlowski2017}.
        EHT is \citet{EHT2019_PaperV}.      }

@@

The plotted values are \verb|CONT1450\_\_LUM| and \verb|BR\_CIV\_1549\_\_\EW|.
\verb|CONT1\_\_LUM| is the $\nu L_{\nu}$ luminosity at wavelength
%{\tt CONT1\_\_WAVE}, and the latter is always within the observed wavelength range, hence it is always present. We use the v1.2.4 of the QSFIT catalogue, applying the cuts: {\tt BR\_CIV\_1549\_\_LUM} $>0$ \&\& {\tt BR\_CIV\_1549\_\_EW} $>0$.
This selects 20,374 quasars.
%On the other hand, CONT1450__LUM is estimated at 1450AA (rest frame), hence it is available only if 1450AA is within the available
%wavelength range.  For SDSS data, CONT1450__LUM is available only if $z> 1.83$.

The slope $\beta$ is $-0.1997$. 
Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
in line with that from \citet{Hamann2017} ($\beta=-0.23$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. %Note the REW logarithmic scaling.
}
  \label{fig:REWvsFWHM}
\end{figure}

%{\bf Our Eddington ratios \\
%Done 1\% \\
%Coatman, Hewett say \civ\ masses are okay.\\
%But what are these Eddington ratios? \\
%Low state BHs vs. High-mass BHs... \\
%Coatman et al?? Blue-shiftted \\ }
\section{Discussion}
The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191104v3.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot. The continuum luminosities are
     from \citet{Kozlowski2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}
\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.

@@

We investigate this reporting the Eddington ratios of the three
quasars in Table~\ref{tab:Eddington_ratios}.

%\subsection{Variability around billion solar mass black holes} 
The Event Horizon Telescope (EHT) mapped the central compact radio
source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI,
EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV,
EHT2019_PaperVI} .

The EHT observsations confirm the observed 1.3mm asymmetric ring
emission is consistent with predictions of strong
gravitational lensing of synchrotron emission from a hot plasma
orbiting near the black hole event horizon \citep{EHT2019_PaperV}.

EHT2017 data includes tracks from four separate
days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
compared to the decorrelation timescale of simulated images, which is
$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
plasma.

From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
\begin{equation}
R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
\end{equation}
giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c =$
32,015 secs (0.37 days).

$\log_{10} (M_{\rm M87^{*}} / M_{\odot} ) = 9.813$.  which is only
about double that of J1205+3422 or J2228+2201, and a factor of $\sim$6
that of J1638+2827.  However, M87 has an Eddington accretion rate of
$\approx$140 $M_{\odot}$ yr$^{-1}$, and thus an Eddington ratio of
$\dot{M} / \dot{M}_{\rm Edd} \sim 2 \times 10^{-5}$, i.e. $\eta_{\rm
Edd} = -4.699$.  \citep[assuming the canonical accretion radiative
efficiency of 10\%; ][]{DiMatteo2003a, EHT2019_PaperV}.

>>>>

For the BOSS spectrum of J2228+2201 on MJD 56189, some of the data are
``masked'' (i.e. they have {\tt and\_mask} != 0) in the FITS file at
wavelengths $\lesssim$1600\AA\ (rest-frame).  This typically means
there is some potential problem in using those data. However, visual
inspection shows strong broad \civ\ emission, so we disable the check on the mask,
and report the line fits in Table~\ref{tab:LineMeasurements} and show the \civ\ line 
fits in~\ref{fig:CIV_LineFits}.

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.4cm 0.4cm 0.2cm 0.4cm, clip]
  {figures/CIV_fits_20191108.png}
   \vspace{-12pt}
   \caption[]{The \civ\ emission line and the subsequent QSFit model and
     parameters.}
\end{figure}

\begin{table*}
  \centering
  % \input{emission_line_comparison_tab}
  \input{emission_line_tab}
  \caption{Line Measurement information for the nine epochs for the 3
    quasars.  Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM
    and $V_{\rm off}$ in km s$^{-1}$, where positive values of $V_{\rm
      off}$ means the line is blueshifted.  Equivalent widths are in units
    of \AA\ .  Positive values of V$_{\rm off}$ means the line is
    blueshifted.  All measuremennts are from QSFIT, except for J1638+2827
    (MJD 54553) which are from \citet{Shen2011}.  $^{(d)}$Emission line
    modelled with two components.}
 \label{tab:LineMeasurements}
\end{table*}

@@

%                              &                                     &                                       &                                               &                             &                                &                  &                  & \\
 %   M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\
  %                                &                                     &                                       &                                               &                             &                                &                  &                  & \\

@@

        Kozl17 is \citet{Kozlowski2017}. }

@@

The plotted values are \verb|CONT1450__LUM| and
\verb|BR_CIV_1549__EW|.  \verb|CONT1__LUM| is the $\nu L_{\nu}$
luminosity at wavelength. This selects 20,374 quasars.  The slope
$\beta$ is $-0.1997$.  Checking with \citet{Kozlowski2017}, using
their bolometric luminosity gives a slope of $\beta=-0.251$, in line
with that from \citet{Hamann2017} ($\beta=-0.23$).
%%
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
nulla. Nullam eu augue id purus mollis dignissim sed et
libero. Phasellus eget justo sed neque pellentesque egestas nec id
arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
neque id mi ultrices tristique. Integer quam libero, ornare vel
gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
cursus, dui nisl egestas augue, non fermentum nisl est nec
nisi. Vestibulum nec mi justo, eget dapibus velit.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. %Note the REW logarithmic scaling.
}
  \label{fig:REWvsFWHM}
\end{figure}
\section{Discussion}
The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191108.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot.
     The continuum luminosities are  from \citet{Calderone2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}
\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.

@@

We investigate this reporting the Eddington ratios of the three
quasars in Table~\ref{tab:Eddington_ratios}.
%%
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
nulla. Nullam eu augue id purus mollis dignissim sed et
libero. Phasellus eget justo sed neque pellentesque egestas nec id
arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
neque id mi ultrices tristique. Integer quam libero, ornare vel
gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
cursus, dui nisl egestas augue, non fermentum nisl est nec
nisi. Vestibulum nec mi justo, eget dapibus velit.
